### 2018-11-16 Sections/optical_encoding_of_quantum_information.tex
QFT complete

In the same way that information can be encoded using the displacement operator via coherent states, we can encode information via the single-mode squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}\in \mathbb{C}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the magnitude of the squeezing and \mbox{$\varphi \in [0, 2\pi]$} denotes that axis along which the squeezing is taking place.

>>>>

In the same way that information can be encoded using the displacement operator via coherent states, we can encode information via the single-mode squeezing operator\index{Squeezing operator},
\begin{align}\label{eq:sq_op}
\hat{S}(\xi) = \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],
\end{align}
where \mbox{$\xi  = r e^{i \varphi}\in \mathbb{C}$}, $r$ is known as the squeezing parameter\index{Squeezing parameter}, which will determine the magnitude of the squeezing, and \mbox{$\varphi \in [0, 2\pi]$} denotes the axis along which the squeezing is taking place.

### 2018-11-16 Sections/physical_architectures_for_quantum_computing.tex
QFT complete

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi\hat{a}_1^\dag\hat{a}_2^\dag + \xi^*\hat{a}_1\hat{a}_2 \right],
\end{align}
where \mbox{$\xi\in \mathbb{C}$} is the squeezing parameter. Both of these may be implemented physically using non-linear crystals\index{Non-linear crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in the position/momentum basis.

@@

\startnormtable
\begin{table*}[!htbp]
\begin{tabular}{ |c|c|c| } 
 \hline
 Qubit model gate &  CV equivalent & Implementation \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$ & Displacement \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat x]$ & Displacement \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ & Single-mode squeezer \& quadrature rotation \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat x^2)]$ & Phase-shift \\
CZ		   & $\hat{U}_\mathrm{CZ}= \exp[\frac{i}{2}\hat x_1 \hat x_2]$ & Two beamsplitters \& two squeezers \\
CNOT 	   & $\hat{U}_\mathrm{CNOT} = \exp[-2i\hat x_1 \hat p_2]$ & CZ \& Hadamards \\
Non-linear           &  \color{blue}$\exp{i t\hat x ^{n\geq 3}}$       &  Probabilistic measurements \\
\hline
\end{tabular}
\captionspacetab \caption{Logical generalisations of a universal gate set to the CV model for quantum computing using squeezed state encoding.\label{tab:CV_gates}}
\end{table*}
\startalgtable

@@

The CV model for quantum computation can be made universal by operating within the cluster state model. As discussed in Sec.~\ref{sec:CSQC}, the basic primitive from which the universality of cluster states arises is the single-qubit teleporter (Fig.~\ref{fig:single_qubit_teleporter}), which enables arbitrary quantum information to be teleported through the substrate state, accumulating the action of single- and two-qubit quantum gates in the process, thereby building up a large, arbitrary quantum computation as measurements proceed. Thus, to demonstrate the universality of the CV model we must simply demonstrate an analogous circuit for single-mode CV state teleportation.

A circuit for a single-mode teleporter is shown in Fig.~\ref{fig:CV_teleporter}. Evidently, it is structurally almost identical to the standard single-qubit teleporter, just swapping out some operations for their direct CV equivalents.

@@

The addition of any non-Gaussian projective measurement allows universal quantum computation using CV cluster states. Another class of such gates is the phase gate\index{Phase gate},
\begin{align}
	\exp(it\hat x^{n}),
\end{align}
where \mbox{$n\geq 3$} (the cubic phase gate\index{Cubic phase gate}). In order to perform universal quantum computation, one needs to implement Hamiltonians of arbitrary degree. In the Heisenberg picture, any Gaussian operation is at most quadratic in the Hamiltonian, and the commutators are also at most quadratic. If one can implement the cubic phase gate, the commutators will now be of degree 3 or 4, and by induction one can construct a Hamiltonian of any degree \cite{bib:kok2010introduction}.

@@

Having demonstrated fault-tolerance, it can be concluded that CV optical quantum computation is viable, and scalable with efficient error correction resource overheads.

>>>>

Mathematically, there are two operators of interest, the single- and two-mode squeezing operators\index{Squeezing operators},
\begin{align}\label{eq:sq_op}
\hat{S}_\mathrm{single}(\xi) &= \exp\left[ \frac{1}{2}(\xi^*\hat{a}^2 - \xi{\hat{a}^{\dag 2}})\right],\nonumber\\
\hat{S}_\mathrm{two}(\xi) &= \exp\left[ \xi\hat{a}_1^\dag\hat{a}_2^\dag + \xi^*\hat{a}_1\hat{a}_2 \right],
\end{align}
where \mbox{$\xi\in \mathbb{C}$} is the squeezing parameter. Both of these may be realised physically using non-linear crystals\index{Non-linear crystals} with second order non-linearities\index{Second order non-linearities}, readily available in present-day labs.

@@

A phase-shifter\index{Phase-shifters}, implementing the unitary operation,
\begin{align}
\hat{R}(\theta) = e^{i\theta \hat{n}},
\end{align}
where \mbox{$\hat{n}=\hat a^\dag \hat a$} is the photon-number operator\index{Photon-number operator}, rotates a state in phase-space by angle $\theta$ about the origin, implementing the transformation between the position and momentum operators,
\begin{align}\label{eq:xp_theta}
\begin{pmatrix}
\hat x_{\theta}\\
\hat p_{\theta}
\end{pmatrix}
=
\begin{pmatrix}\cos\theta & \sin\theta \\
-\sin\theta & \cos\theta
\end{pmatrix}
\begin{pmatrix}
\hat x\\
\hat p
\end{pmatrix}.
\end{align}
It is evident upon inspection that this can be thought of as a single-qubit rotation in position/momentum space.

@@

\startnormtable
\begin{table*}[!htbp]
\begin{tabular}{ |c|c|c| } 
 \hline
 Qubit model gate &  CV equivalent & Implementation \\ 
  \hline\hline
 Pauli $X$ & $\hat{X}(s) = \exp[-i s \hat p]$ & Displacement \\ 
 Pauli $Z$ & $\hat{Z}(t) = \exp[i t \hat x]$ & Displacement \\ 
 Phase gate & $\hat{P}(\eta) = \exp[i \eta \hat x^2]$ & Single-mode squeezer \& quadrature rotation \\
Hadamard   & $\hat{F}=\exp[i \frac{\pi}{8}(\hat p^2+\hat x^2)]$ & Phase-shift \\
CZ		   & $\hat{U}_\mathrm{CZ}= \exp[\frac{i}{2}\hat x_1 \hat x_2]$ & Two beamsplitters \& two squeezers \\
CNOT 	   & $\hat{U}_\mathrm{CNOT} = \exp[-2i\hat x_1 \hat p_2]$ & CZ \& Hadamards \\
Non-linear phase gate &  $\hat{U}_\mathrm{NL}=\exp[i t\hat{x}^n],\,n\geq 3$       &  Probabilistic measurements \\
\hline
\end{tabular}
\captionspacetab \caption{Logical generalisations of a universal gate set to the CV model for quantum computing using squeezed state encoding.\label{tab:CV_gates}}
\end{table*}
\startalgtable

@@

The CV model for quantum computation can be shown to be universal by operating within the cluster state model. As discussed in Sec.~\ref{sec:CSQC}, the basic primitive from which the universality of cluster states arises is the single-qubit teleporter (Fig.~\ref{fig:single_qubit_teleporter}), which enables arbitrary quantum information to be teleported through the substrate state, accumulating the action of single- and two-qubit quantum gates in the process, thereby building up a large, arbitrary quantum computation as measurements proceed. Thus, to demonstrate the universality of the CV model we must first demonstrate an analogous circuit for single-mode CV state teleportation.

An optical circuit for a single-mode teleporter is shown in Fig.~\ref{fig:CV_teleporter}. Evidently, it is structurally almost identical to the standard single-qubit teleporter, just swapping out some operations for their direct CV equivalents.

@@

The addition of any non-Gaussian projective measurement allows universal quantum computation using CV cluster states. A class of such gates is the non-linear phase gate\index{Non-linear phase gate},
\begin{align}
	\hat{U}_\mathrm{NL}=\exp(it\hat x^{n}),
\end{align}
where \mbox{$n\geq 3$} (the cubic phase gate\index{Cubic phase gate}).

In order to perform universal quantum computation, one needs to implement Hamiltonians of arbitrary degree. In the Heisenberg picture, any Gaussian operation is at most quadratic in the Hamiltonian, and the commutators are also at most quadratic. If one can implement the cubic phase gate, the commutators will now be of degree 3 or 4, and by induction one can construct a Hamiltonian of any degree \cite{bib:kok2010introduction}.

@@

Having demonstrated fault-tolerance, it can be concluded that CV optical quantum computation is viable, and scalable, with efficient error correction resource overheads.

### 2018-11-16 Sections/quantum_algorithms.tex
minor
QFT complete

The quantum Fourier transform (QFT) is not an algorithm per se, but rather a unitary operator that finds widespread use in other quantum algorithms. The QFT operator is so ubiquitous that it warrants special treatment.

@@

Unlike the closely-related Hadamard transform\index{Hadamard!Transform}, $\hat{H}^{\otimes n}$, which shares many properties with the QFT, the QFT is a highly entangling operation. The QFT of any dimension has an efficient circuit implementation, making it an important subroutine in many algorithms. Specifically, the $n$-qubit QFT (i.e a transformation on $2^n$ amplitudes) requires only $O(n^2)$ elementary gates (Hadamards and CZs). If an approximation of the QFT is sufficient for one's purposes, this can be further reduced to only \mbox{$O(n\,\log \,n)$}.

\comment{Show algorithm box with circuit}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid.}
\end{figure}

>>>>

The quantum Fourier transform (QFT) is not an algorithm per se, but rather a unitary operator that finds widespread use in other quantum algorithms -- a quantum subroutine of sorts. The QFT operator is so ubiquitous as a component in other quantum algorithms, that it warrants special treatment.

@@

Unlike the closely-related Hadamard transform\index{Hadamard!Transform}, $\hat{H}^{\otimes n}$, which shares many properties\footnote{Like the QFT, all matrix elements of the Hadamard transform have magnitude \mbox{$1/\sqrt{N}$}, differing only in their phases, which are all simple $\pm$.} with the QFT, the QFT is a highly entangling operation. The QFT of any dimension has an efficient circuit implementation, making it an important subroutine in many algorithms. Specifically, the $n$-qubit QFT (i.e a transformation on $2^n$ amplitudes) requires only $O(n^2)$ elementary gates (Hadamards and CZs). If an approximation of the QFT is sufficient for one's purposes, this can be further reduced to only \mbox{$O(n\log n)$}.

The circuit construction for the QFT is shown in Fig.~\ref{fig:QFT_circuit}.

\begin{figure}
\includegraphics[width=0.475\textwidth]{QFT}
\caption{Circuit decomposition for the quantum Fourier transform (QFT). The circuit is defined recursively, defining the $n$-qubit QFT in terms of an \mbox{$n-1$}-qubit QFT. Here \mbox{$R_\theta=\mathrm{diag}(1,e^{i\theta})$} is a generalised phase-flip gate.}\label{fig:QFT_circuit}\index{Quantum Fourier transform}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and $C_Z$ gates are drawn in red.}
\end{figure}
